Manuscript Figures

### 2020-06-17 doc/MS_Figures_v2.rmd
updating some Figures

  labs(y = "Total SC Length")+ylim(c(1000,2600 ))+ggtitle("")

@@

## Fig Chrm Proportion plot

@@

chrm.class.barplot.final <- addSmallLegend(chrm.class.barplot)

@@

>>>>

  labs(y = "Total SC Length")+ylim(c(1000,5000 ))+ggtitle("")

@@

#Fig 4 Proportions
## Fig Chrm Proportion plot

@@

chrm.class.barplot.final <- addSmallLegend(chrm.class.barplot)
#this legend is too small and fuzzy in figures
```

@@

```{r Q1.show.SC.length, echo=FALSE, warning=FALSE, eval=FALSE}
#switch the cleanCurated_BivData

#nested boxplots, pooled Bivalents
Q1.SC.length_Nested_boxplots_Dom <- ggplot(cleanCurated_BivData[cleanCurated_BivData$subsp == "Dom",], aes(y = chromosomeLength, x=strain, fill=as.factor(hand.foci.count) ))+geom_boxplot(alpha=0.5)+ggtitle("Bivalent SC Lengths by Chrm Class \n Dom")+facet_wrap(subsp~sex, scales="free")+ylim(c(25,255))+theme(legend.position="none")

```{r Q1.show.IFD.scatter, echo=FALSE, eval=FALSE, message=FALSE}

#these are the scatter plots

nrm.IFD_KAZ_long <- ggplot( (Q1.IFD.long %>% filter(strain =="KAZ" ) ) , aes(y = meanIFD2CO_norm, x= sex,color=mouse))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")

nrm.IFD_KAZ_BIV.long <- ggplot( (real.long.bivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2")  ) , aes(y = IFD1_PER, x= sex, color=mouse))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")
#11jan18_KAZ_m3, 26jan18_11jan18_KAZ_m3_sp1_8_rev_19
#looked up image, measures confirmed

####
nrm.IFD_KAZ_short <- ggplot( (Q1.IFD.short %>% filter(strain =="KAZ" ) ) , aes(y = meanIFD2CO_norm, x= sex,color=mouse))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")

nrm.IFD_KAZ_BIV.short <- ggplot( (real.short.bivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2")  ) , aes(y = IFD1_PER, x= sex, color=mouse))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")
#21may18_KAZ_m2 -- seems like it might be an outlier
#5jun18_21may18_KAZ_m2_sp1_19.2_rev_16
#second foci slightly smaller, kinda fainter -- but also much brighter than background

#check all KAZ males

nrm.IFD_KAZ_BIV.data <- ggplot( (cleanCurated_BivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

nrm.IFD_KAZ.female_BIV.data <- ggplot( (cleanCurated_BivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "female")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, female KAZ")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))
nrm.IFD_KAZ.female_BIV.data

nrm.IFD_PWD.female_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="PWD" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "female")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, female PWD")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))
nrm.IFD_PWD.female_BIV.data

nrm.IFD_LEW.female_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="LEW" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "female")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, female LEW")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))
nrm.IFD_LEW.female_BIV.data

nrm.IFD_G.female_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="G" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "female")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, female G")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))
nrm.IFD_G.female_BIV.data

nrm.IFD_WSB.female_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="WSB" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "female")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, female WSB")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))
nrm.IFD_WSB.female_BIV.data    #18nov17_WSB_f2 has continuous ifd range

nrm.IFD_LEW_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="LEW" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS LEW")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

nrm.IFD_MOLF_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MOLF" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS MOLF")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))+theme(axis.text.x = element_blank())

raw.IFD_MOLF_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MOLF" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_ABS, x= mouse, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS MOLF")+theme(axis.text.x = element_blank())+ylim(c(0, 100))

raw.IFD_MSM_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MSM" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_ABS, x= mouse, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS MSM")+theme(axis.text.x = element_blank())+ylim(c(0, 100))

Fby.F.IFD_MOLF_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MOLF" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = Foci1, x=Foci2, color=chromosomeLength))+geom_point()+ggtitle("FOce Pos by Fos Pos MOLF")+facet_wrap(~mouse, scales = "free")+ylim(c(0,75))+xlim(c(0,120))+theme(legend.position="none")

Fby.F.IFD_MSM_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MSM" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = Foci1, x=Foci2, color=chromosomeLength))+geom_point()+ggtitle("Foci Pos by Fos Pos MSM")+facet_wrap(~mouse, scales = "free")+ylim(c(0,75))+xlim(c(0,120))+theme(legend.position="none")

###look at why KAZ males are weird
nrm.IFD_KAZ_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, male KAZ")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))+theme(axis.text.x = element_blank(), legend.position = "none")

nrm.IFD_LEW_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="LEW" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, male LEW")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

#the difference the the Nrm IFD cut off is striking with these plots
nrm.IFD_PWD_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="PWD" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male") ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, male PWD")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

nrm.IFD_MSM_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MSM" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, male GMSM")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

nrm.IFD_SKIVE_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="SKIVE" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, male SKIVE")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

nrm.IFD_G_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="G" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, male G")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))

nrm.IFD_sex.comp_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="LEW" ) %>%  filter(hand.foci.count == "2") ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, ")+facet_wrap(~sex, scales = "free")+ylim(c(0,1))+theme(legend.position="none",axis.text.x = element_blank())

```{r Q1.IFD_show.IFD_99, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

#first draft of the IFD comparisons
#make the mouse boxplots -- instead of geom_points

#Only use 2CO bivalents
Curated_BivData.22 <- Curated_BivData[Curated_BivData$hand.foci.count == 2,]
Curated_BivData.22 <- Curated_BivData.22[(!is.na(Curated_BivData.22$hand.foci.count)),]

P1.by.P2_plot <- ggplot(Curated_BivData.22, aes(y = rev(PER_Foci_2), x= PER_Foci_1, color=strain))+
  geom_jitter(alpha=.2)+
  ggtitle("Normalized IFD")+
  scale_color_manual(values=colors_of_strains)+  facet_wrap(sex~subsp, scales = "free")+theme(legend.position="none")+xlim(c(0,1))+ylim(c(0,1))

#each point is a 2CO, with the F1 and F2 position 
#based on plot from Dourad et al (Mercier)

P1.by.P2_plot_raw.WSB <- ggplot(Curated_BivData.22 %>% filter(strain == "LEW"),
    aes(y = Foci2, x= Foci1, color=strain))+
  geom_jitter(alpha=.5)+
  ggtitle("Raw IFD WSB")+
  scale_color_manual(values=colors_of_strains)+  facet_wrap(sex~subsp, scales = "free")+theme(legend.position="none") + ylim(c(0,160))+xlim(c(0,160))+ theme(  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank() )

#trying to move x axis to top
#cowplot might be the easier way -- since kinda diffecult in ggplot
#or ggdraw

P1.by.P2_plot_nrm.PWD.f <- ggplot(Curated_BivData.22 %>% filter(strain == "PWD") %>% filter(sex == "female"),
    aes(y = PER_Foci_2, x= PER_Foci_1, color=strain))+
  geom_jitter(alpha=.5)+
#  scale_x_continuous(position = "top") +
  scale_x_continuous(sec.axis = dup_axis(), position = "top")+
    ggtitle("Nrm IFD PWD, female")+scale_color_manual(values=colors_of_strains)+ ylim(c(0,1))+xlim(c(0,1))+ theme(  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank() )

P1.by.P2_plot_nrm.PWD.male <- ggplot(Curated_BivData.22 %>% filter(strain == "PWD") %>% filter(sex == "male"),
    aes(y = PER_Foci_2, x= PER_Foci_1, color=strain))+
  geom_jitter(alpha=.5)+
#  scale_x_continuous(position = "top") +
  scale_x_continuous(sec.axis = dup_axis(), position = "top")+
    ggtitle("Nrm IFD PWD, male")+scale_color_manual(values=colors_of_strains)+ ylim(c(0,1))+xlim(c(0,1))+ theme(  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank() )

#boxplots
boxplots_first.IFD.plot_ABS <- ggplot(Curated_BivData.22, aes(y = IFD1_ABS, x= mouse, color=strain))+geom_boxplot(alpha=.2)+
  geom_jitter(alpha=.2)+
  ggtitle("Interfocal Distances, ABS")+
  scale_color_manual(values=colors_of_strains)+  facet_wrap(sex~subsp, scales = "free")+ylim(c(20,160))+theme(legend.position="none")
#order is out of wack, but -- good for now

boxplots_first.IFD.plot_PER <- ggplot(Curated_BivData.22, aes(y = IFD1_PER, x= mouse, color=strain))+geom_boxplot(alpha=.2)+
  geom_jitter(alpha=.2)+
  ggtitle("Interfocal Distances, PER")+
  scale_color_manual(values=colors_of_strains)+  facet_wrap(sex~subsp, scales = "free")+theme(legend.position="none")+ylim(c(0,1))

first.IFD.plot_ABS <- ggplot(Curated_BivData.22, aes(y = IFD1_ABS, x= strain, color=mouse))+geom_jitter()+ggtitle("Interfocal Distances, ABS")+facet_wrap(sex~subsp, scales = "free")+ylim(c(20,160))+theme(legend.position="none") #+scale_color_manual(values=colors_of_strains)

first.IFD.plot_PER <- ggplot(Curated_BivData.22 %>% filter(chromosomeLength < 150), aes(y = IFD1_PER, x= strain, color=chromosomeLength))+geom_jitter()+ggtitle("Interfocal Distances, PER \ncut off of chrm lengths, 150")+facet_wrap(sex~subsp, scales = "free")+ylim(c(0,1))

#+theme(legend.position="none")
```

```{r Q2.SC.long.biv_plots, echo=FALSE, eval=FALSE}

#REAL.long_mouse_table
#REAL.short_mouse_table

#real.long.bivData
#real.short.bivData

shoo.long.biv <- ggplot( (real.long.bivData %>% filter(sex == "male") ), aes(y=chromosomeLength, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Single Biv \nMale Long Biv SC Lengths")

#cell.avlong.biv <- ggplot(cell.av.long.biv.table, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Cell av. \nMale Long Biv SC Lengths")

mouse.shoo.long.biv <- ggplot( REAL.long_mouse_table, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + ggtitle("Mouse av. \nMale Long Biv SC Lengths")

#cell.avlong.biv <- ggplot( cell.av.long.biv.table, aes(y=mean.sc, x=strain, color=strain))+geom_jitter()+facet_wrap(~subsp, scales = "free")+scale_color_manual(values=colors_of_strains)+ylim(c(75,140))+geom_boxplot(alpha=.2) + #ggtitle("Cell av. \nMale Long Biv SC Lengths")

```{r Q2_tot.sc_plot, echo=FALSE, warning=FALSE}

mouse.av_totsc_male <- ggplot(data= mouse.total.skel %>% filter(sex == "male"), aes(y = mean.skel, x=mouse, color=strain))+ geom_point()+scale_color_manual(values=colors_of_strains)+
  facet_wrap(Rec.group~subsp, scales="free")+
  theme(axis.title.x=element_blank(),  axis.text.x=element_blank(), axis.text.y = element_text(size=9), axis.ticks.x=element_blank(), legend.position = c(0.8, 0.2) ) + ylim(c(1200,1850 ) )+labs(y="Mouse Mean Total SC")

mouse.av_totsc_male <- addSmallLegend(mouse.av_totsc_male)
